\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-28 tex/ms.tex
Boom

@@

In this work, we build on this methodological foundation to perform 
reflected-light mapping of planetary surface features on Sol d. 
We give an overview of the \TESS data used in Section \ref{sec:data}. 
In Section \ref{sec:methods}, we describe the methods employed to infer a map 
from these data, including the adaptation of the \starry algorithm to reflection 
mapping, the modeling of spacecraft-related systematics, and the likelihood and 
priors used. 
We present results in Section \ref{sec:results} and make comparison of these 
findings to state-of-the-art terrestrial planet maps from the literature in 
Section \ref{sec:discussion}. 
Finally, we conclude in Section \ref{sec:conclusion} with a look at future 
prospects for phase-curve mapping of terrestrial exoplanets.

@@

For each of the two sectors considered, we downloaded a randomized subsample of 1000 short-cadence lightcurve files corresponding to postage stamps located across the full \TESS field of view and extracted the background flux time series from each. 
Not all postage stamps are equally informative, since the desired signal from Sol d is inhomogenously spread across the \TESS detectors and manifests differently in different regions (see Section \ref{sec:systematics}). 
We down-selected our pool of 1000 targets to 75 maximally useful background lightcurves from Sector 1 and 20 from Sector 2. 
This down-selection was done with several criteria in mind: each lightcurve should contain a significant signal from Sol d; they should be representative of the general background flux modulation seen across the \TESS cameras, rather than containing any truly localized signals from astrophysical background sources; and the sample as a whole should contain the full range of typical behaviors of background across the entire \TESS field of view. 
To accomplish this, we... \todo{(decide whether it's outlier rejection only or full-on categorization)}

@@

As we discussed above, light curve inversion is a hard problem,
and we have shown that this is true even when the solution is
known ahead of time. Presented with the top panel of Figure~\ref{fig:map}
(without the continent outlines),
an inhabitant of Sol d would be hard-pressed to identify that
as a map of their home planet. This is in part due to the biases
in our optimization, which we discussed above, but also due to the 
simple fact that the reflectance of Sol d is dominated---by far---by 
time-variable clouds. While stationary cloud features on Sol d are
typically associated with continents (the most pronounced cloud features
being over South America, Africa, and south Asia), persistent cloud
cover can occur over open ocean, as seen in the north Pacific
in Figure~\ref{fig:map}. Given a baseline of just a few weeks, it is
not possible to tell the difference between highly reflective land
features (such as ice or vegetation) and stationary clouds.

We should not expect other exoplanets in the habitable zone to be
any different.

\todo{Discuss how this problem is *hard* and how we need
large time baseline to disentangle clouds from continents, and even
then there are cloud features that are stationary, so hard to
tell apart. What we really need is multi-band photometry,
as suggested in \cite{Cowan2009}.}

\section{Conclusion}
\label{sec:conclusion}

>>>>

\todo{We need to cite \cite{Sagan1993}!}

@@

In this work, we build on this methodological foundation to perform 
reflected-light mapping of planetary surface features on Sol d. 
We give an overview of the \TESS data used in \S\ref{sec:data}. 
In \S\ref{sec:methods}, we describe the methods employed to infer a map 
from these data, including the adaptation of the \starry algorithm to reflection 
mapping, the modeling of spacecraft-related systematics, and the likelihood and 
priors used. 
We present results in \S\ref{sec:results} and make comparison of these 
findings to state-of-the-art terrestrial planet maps from the literature in 
\S\ref{sec:discussion}. 
Finally, we conclude in \S\ref{sec:conclusions} with a look at future 
prospects for phase-curve mapping of terrestrial exoplanets.

@@

For each of the two sectors considered, we downloaded a randomized subsample of 1000 short-cadence lightcurve files corresponding to postage stamps located across the full \TESS field of view and extracted the background flux time series from each. 
Not all postage stamps are equally informative, since the desired signal from Sol d is inhomogenously spread across the \TESS detectors and manifests differently in different regions (see \S\ref{sec:systematics}). 
We down-selected our pool of 1000 targets to 75 maximally useful background lightcurves from Sector 1 and 20 from Sector 2. 
This down-selection was done with several criteria in mind: each lightcurve should contain a significant signal from Sol d; they should be representative of the general background flux modulation seen across the \TESS cameras, rather than containing any truly localized signals from astrophysical background sources; and the sample as a whole should contain the full range of typical behaviors of background across the entire \TESS field of view. 
To accomplish this, we... \todo{(decide whether it's outlier rejection only or full-on categorization)}

@@

As we discussed above, light curve inversion is a hard problem,
and we have shown that this is true even at high signal-to-noise and 
when the solution is
known ahead of time. Presented with the top panel of Figure~\ref{fig:map}
(without the continent outlines),
an inhabitant of Sol d may be hard-pressed to identify that
as a map of their home planet. This is in part due to the biases
in our optimization, which we discussed above, but also due to the 
simple fact that the reflectance of Sol d is dominated---by far---by 
time-variable clouds. While stationary cloud features on Sol d are
typically associated with continents (the most pronounced cloud features
being over South America, Africa, and south Asia), persistent cloud
cover can occur over open ocean, as seen in the north Pacific
in Figure~\ref{fig:map}. Given a baseline of just a few weeks, it is
not possible to tell the difference between highly reflective land
features (such as ice or vegetation) and stationary clouds.

We should not expect other exoplanets in the habitable zone to be
any different. Future missions such as LUVOIR or HabEx may enable
us to collect data on the phase curves of such planets, but that
data will be of signficantly lower quality and poorer time resolution,
so the work presented here can be seen as an upper limit on what we may
be able to infer about exoplanets in the habitable zone with
next-generation facilities.

That said, the time baseline considered in this work was fairly
limited---three weeks in Sector 1 and one week in Sector 2,
spanning two months in total. Observations taken throughout an entire
year on Sol d---during which time cloud patterns should change with the
seasons and the angle between the day/night terminator and the 
axis of rotation should precess---may help to disambiguate between
clouds, oceans, and continents. We intend to perform this analysis
in upcoming work once data from future \tess sectors becomes available.

Alternatively, time-resolved observations in multiple bands could
also help with this problem. This was discussed in \cite{Cowan2009},
who showed that multi-band photometry of the Earth enables one to
disentangle the contributions from oceans, continents, and cloud cover.
A robust detection of surface features on an exoplanet in the habitable
zone will likely necessitate both approaches alongside a circumspect
analysis of the uncertainties and degeneracies at play.

\section{Conclusions}
\label{sec:conclusions}
